Verifying Demonstrations

### 2018-08-30 paper/DB-anon-cred.tex
more items

In the original \ac{DB} paper by \citet{DistanceBounding}, one of the distance-bounding protocol is based on the Schnorr identification scheme~\cite{Schnorr}.
However, this \ac{DB} Schnorr protocol was shown to be prone to distance hijacking~\cite{DistanceHijacking}, in addition to not being secure against terrorist fraud.
We now propose another way to turn the Schnorr protocol into a
public-key \ac{DB} protocol which is secure against \ac{DBMF},
\ac{DBDF}, \ac{DBDH} and \ac{DBTF}.
The public-key property implies protection against an impersonating
verifier.

@@

\ac{DBIF} resistance follows from Schnorr.\sonja{Daniel, please
  complete this sentence:, our changes don't break Schnorr because ...}
Finally, a malicious verifier who wants to impersonate a prover can guess the 
remaining \(|q|-l\) bits after the protocol finished to compute the secret of 
the prover.
The probability that this succeeds is, as above,
\(2^{-(|q|-l)}\). While the majority of \ac{DB} schemes are based on
shared secrets and thus assume an honest verifier, this limits the
inherent advantage of our public-key
\ac{DB} scheme.

>>>>

In the original \ac{DB} paper by \citet{DistanceBounding}, one of the distance-bounding protocol is based on the Schnorr identification scheme~\cite{Schnorr}.
However, this \ac{DB} Schnorr protocol was shown to be prone to distance hijacking~\cite{DistanceHijacking, TamarinDB}, in addition to not being secure against terrorist fraud.
We now propose another way to turn the Schnorr protocol into a
public-key \ac{DB} protocol which is secure against \ac{DBMF},
\ac{DBDF}, \ac{DBDH} and \ac{DBTF}.
The public-key property implies protection against an impersonating
verifier.

@@

\ac{DBIF} resistance follows from Schnorr.\sonja{Daniel, please
  complete this sentence:, our changes don't break Schnorr because ...}
Finally, a malicious verifier who wants to impersonate a prover can guess the 
remaining \(|q|-l\) bits after the protocol finished to compute the secret of 
the prover.
The probability that this succeeds is, as above,
\(2^{-(|q|-l)}\). While the majority of \ac{DB} schemes are based on
shared secrets and thus assume an honest verifier, this limits the
inherent advantage of our public-key
\ac{DB} scheme.  \sonja{verifier impersonating prover: vulnerability
  we introduce against public-key DB schemes, mitigated by limiting
  size of l (bits of other s). Trade-off: want long l for reducing
  success of guessing correct sequence of challenge bits, want short l
  for reducing success of guessing the other s and finding alpha}

\sonja{\subsection{Formal Verification} 
 verification with tamarin: there is no BC Schnorr in Tamarin,  [10]
assumed equivalence with Fiat-Shamir model. Not straightforward to
implement Schnorr in Tamarin due to a lack of expressiveness for
arithmetic needed to complement Diffie-Hellman. If not done now, left
for future work. }

### 2018-08-30 paper/conclusions.tex
more items

In this paper, we have introduced \PRIVO, a privacy-preserving protocol for verifiably counting participants at protests. 
Despite the verification, the privacy of the participants is preserved to the extent possible by their physical presence at the protest. 
To achieve that, we adapted the Schnorr protocol to develop distance-bounding anonymous credentials. \sonja{Rephrase the following after we have requirements and results:
Except for receipt freeness, which we cannot guarantee if the adversary gets access to Alice's device and secret PRF key after her participation has been witnessed and before she had a chance to delete it, \PRIVO fulfills all verification and privacy properties we derived from those of electronic voting complemented by the specific constraints on time and location required for protests. }

@@

In general, none of the related works fulfills the eligibility
verifiability (one proof per person, temporal and spatial eligibility ---
\cref{%
  CountOnce,%
  TemporallyRelated,SpatiallyRelated,%
}).
To some extent, some techniques do fulfill designated event (\cref{DesignatedEvent}), since people usually use placards in the protests.
Also, some schemes provide universal verifiability (\cref{UniversalVerif}), but not individual verifiability (\cref{IndividualVerif}).
Moreover, if they provided individual verifiability, they would likely violate the privacy requirements.

Finally, most of the current methods are estimates, with quite some error margins. 
While \PRIVO is an actual count and not an estimate, its accuracy for the total number of participants hinges on the participants having the necessary equipment (\ie, a smartphone or similar device), some sort of trustworthy credential, and the willingness to run the protocol. 
Owing to the network effect, until used by most participants, \PRIVO would result in a considerable undercount. 
However, it represents a first step toward accurate verifiable yet privacy-preserving crowd counting by showing how it can be done in theory at least and in practice once some assumptions concerning hardware and e-identities become more realistic. 
While the the necessary technologies are not yet available in most authoritarian regimes, some of them are in several democracies. We believe that it is important to implement systems such as ours also there to support the maintenance of democratic processes.

>>>>

In this paper, we have introduced \PRIVO, a privacy-preserving protocol for verifiably counting participants at protests. 
Despite the verification, the privacy of the participants is preserved to the extent possible by their physical presence at the protest. 
To achieve that, we adapted the Schnorr protocol to develop distance-bounding anonymous credentials. \sonja{Rephrase the following after we have requirements and results:
Except for receipt freeness, which we cannot guarantee if the adversary gets access to Alice's device and secret PRF key after her participation has been witnessed and before she had a chance to delete it, \PRIVO fulfills all verification and privacy properties we derived from those of electronic voting complemented by the specific constraints on time and location required for protests. }
With respect to privacy, \PRIVO provides anonymity (of participants)  and unlinkability (between protests) unless the adversary gets access to the private key/ID or has side information (she also needs the private key for proof of the cause (cid) supported by the protester, otherwise she does not learn more than without \PRIVO).

@@

In general, none of the related works fulfills the eligibility
verifiability (one proof per person, temporal and spatial eligibility ---
\cref{%
  CountOnce,%
  TemporallyRelated,SpatiallyRelated,%
}).
To some extent, some techniques do fulfill designated event (\cref{DesignatedEvent}), since people usually use placards in the protests.
Also, some schemes provide universal verifiability (\cref{UniversalVerif}), but not individual verifiability (\cref{IndividualVerif}).
Moreover, if they provided individual verifiability, they would likely violate the privacy requirements.
\sonja{Daniel, explain the previous sentence, is that from you?}
Finally, most of the current methods are estimates, with quite some error margins. 
While \PRIVO is an actual count and not an estimate, its accuracy for the total number of participants hinges on the participants having the necessary equipment (\ie, a smartphone or similar device), some sort of trustworthy credential, and the willingness to run the protocol. 
Owing to the network effect, until used by most participants, \PRIVO would result in a considerable undercount. 
However, it represents a first step toward accurate verifiable yet privacy-preserving crowd counting by showing how it can be done in theory at least and in practice once some assumptions concerning hardware and e-identities become more realistic. 
While the the necessary technologies are not yet available in most authoritarian regimes, some of them are in several democracies. We believe that it is important to implement systems such as ours also there to support the maintenance of democratic processes.

### 2018-08-30 paper/protocol.tex
Fixes PLR's comment on proof-of-personhood and collective signing
more items

Several entities are involved in our protocol.
First, \iac{CA} is responsible for certifying a one-to-one mapping between a 
person's identity and a cryptographic key\footnote{%
  This can be done by a centralized authority, such as a nation state with, 
  \eg, passports; or a decentralized authority, as in the case of 
  proof-of-personhood~\cite{proof-of-personhood}.
}.
The \ac{CA} is only involved in the setup phase.
Second, a participant is an individual who wants to participate in a given 
protest.
A participant can assume three different roles:
\begin{enumerate}
\item The \emph{organizer} has written a manifesto for the protest and forward it to others.
\item A \emph{protester} is attending the protest and asks witnesses to vouch 
  for his presence.
\item A \emph{witness} provides proofs to protesters which state that the 
  protester was indeed participating and such that the proofs are verifiable by 
  third parties.
\end{enumerate}
In general, there is one organizer and every participant can act alternatively 
as both protester and witness.

@@

\begin{figure}
  \centering
  %\footnotesize
  \includegraphics{proofshare.tikz}
  \caption{%
    Structure of a proof share.
    The protest (cause) identifier \(\cid\) is the hash value of the manifesto.
    The protester \(P\)'s identifier \(\pid\) is computed using the protester's key \(\sk_P\) and \(\cid\).
    The witness \(W\)'s identifier \(\wid\) is computed using the
    witness's key \(\sk_W\) and the protester's \(\pid\).
    \(t_s, t_s'\) are the last heads of the blockchain seen by the protester and witness, respectively, and \(l\) is an area.
    All values are signed by the witness (signature \(\prf_W\)) while also 
    proving the correctness of \(\wid\) and knowledge of a signature on 
    \(\sk_W\).
    The protester constructs \(\prf_P\) analogously.
  }%
  \label{fig:ProofFig}
\end{figure}%

>>>>

Several entities are involved in our protocol.
First, \iac{CA} is responsible for certifying a one-to-one mapping between a 
person's identity and a cryptographic key\footnote{%
  This can be done by a centralized authority, such as a nation state with, 
  \eg, passports; or a decentralized authority, as in the case of a a 
  collective authority~\cite{collective-signing} powered by 
  proof-of-personhood~\cite{proof-of-personhood}.
}.
The \ac{CA} is only involved in the setup phase.
Second, a participant is an individual who wants to participate in a given 
protest.
A participant can assume three different roles:
\begin{enumerate}
\item The \emph{organizer} has written a manifesto for the protest and forward it to others.
\item A \emph{protester} is attending the protest and asks witnesses to vouch 
  for his presence.
\item A \emph{witness} provides proofs to protesters which state that the 
  protester was indeed participating and such that the proofs are verifiable by 
  third parties.
\end{enumerate}
In general, there is one organizer and every participant can act alternatively 
as both protester and witness.

@@

\begin{figure}
  \centering
  %\footnotesize
  \includegraphics{proofshare.tikz}
  \caption{%
    Structure of a proof share.
    The protest (cause) identifier \(\cid\) is the hash value of the manifesto.
    The protester \(P\)'s identifier \(\pid\) is computed using the protester's key \(\sk_P\) and \(\cid\).
    The witness \(W\)'s protester-specific identifier \(\wid\) is computed using the
    witness's key \(\sk_W\) and the protester's \(\pid\).
    \(t_s, t_s'\) are the last heads of the blockchain seen by the protester and witness, respectively, and \(l\) is an area.
    All values are signed by the witness (signature \(\prf_W\)) while also 
    proving the correctness of \(\wid\) and knowledge of a signature on 
    \(\sk_W\).
    The protester constructs \(\prf_P\) analogously.
  }%
  \label{fig:ProofFig}
\end{figure}%
